Manifold fitting by ridge estimation: a subspace-constrained approach

### 2021-02-25 rebuttal/response-referee1.tex

\begin{center}
{\bf \large Point-by-Point Response to Referee One}
\end{center}
Thank you very much for your careful reading our paper as well as your invaluable comments. We list our response to your comments as follows:\\ 
major comments\\

\noindent ``\textit {This paper is on manifold learning.  It is very confusing to read.''}\\
Answer:\\
To the best of our knowledge, manifold learning refers to an approach to non-linear dimensionality reduction, which is a method trying to find the new representation in a lower-dimensional space by approximately keeping the geometry properties of the input which resides in a high-dimensional ambient space. In this paper, we learn the original manifold in the ambient space. Therefore, our work is not on manifold learning.

\noindent ``\textit{For example, realistically the data generated by the manifold model are generated with noise, and the distribution and properties of the noise in conjunction with the reach of the manifold are critical for the recovery. However, these critical issues are bypassed by making strong assumptions whereby only the local behavior of ridges matters.''}\\
Answer:\\
We agree with the referee that the recovery is highly related with the noise and reach of the manifold. In our work, our model in Equation (1) on page assumes the data are generated as 
\begin{equation}\label{model}
x_i=\tilde{x}_i+\epsilon_i,
\end{equation}
where $\tilde{x}_i$ is the noiseless signal which belong to some manifold, and $\epsilon_i$ is the noise. We use the observations $x_i$ to recover the manifold. Therefore, we did not bypass consideration of the noise in our model.
\\
The reach is a global concept which describes the degree of curvature for the manifold. A larger {``\it reach''} indicates the samples resides further from the manifold can also has a unique projection onto $\cal M$. Therefore, the manifold is more flat globally.

\noindent ``\textit{ This approach may be interesting in its own rights, but the impact in the bigger picture is rather limited due to the limited perspective and the strong assumptions that are needed. The best part are the computational perspectives provided in the paper, while the theoretical developments are also not very interesting.'' }\\
Answer:\\
In fact, Assumption 2.2 is more likely to be regarded as a ``Claim'' rather than an Assumption. The main intention of Assumption 2.2 is to say that any low-dimensional manifold can be thought as the ridge of some unknown density function. In this new version of the manuscript, we modify the presentation of Assumption 2.2 to avoid the confusion.
\\
\noindent ``\textit {A key problem is that the errors in the sampling of the data generated by the manifold are not modeled and the noise-contaminated data are not studied. The paper is not well written, the presentation is substandard  and is unfocused.'' }\\
Answer:\\
As in Equation \eqref{model}, we model the data as the noiseless $\tilde{x}_i\in \cal M$ plus the noise $\epsilon_i$. We consider the noise in the theories and all the cases of the numerical experiments.\\

### 2021-02-25 Ridge_Estimation_main/Ridge-final.tex
zzh

For each point $\hat{x}$ belonging to ${\cal \hat{G}}$ or ${\cal \hat{G}}_\ell$, we can define the projection of $\hat{x}$ onto the real manifold $\mathcal M$ as $\pi_{\mathcal M}(\hat{x}) = \arg\min_{y\in \mathcal M} \|y-\hat{x}\|_2$. In the case of the special two-dimensional circle, the projection has an explicit form, $\pi_{\mathcal M}(\hat{x}) = \hat{x}/\|\hat{x}\|$. The average margin from $\cal \hat{G}$ or ${ \cal \hat{G}}_\ell$ to $\mathcal M$ is defined as
\[
{\rm Margin}({ \cal \hat{G}, \mathcal M}) =\frac{1}{|{\cal \hat{G}}|}  \sum_{x_k\in  {\cal \hat{G}}} \min_{y\in \mathcal M}\|x_k-y\|_2.
\]
\begin{figure}[t] %  figure placement: here, top, bottom, or page
   \includegraphics[width=\linewidth]{circle8n.eps} 
   \includegraphics[width=\linewidth]{sphere8.eps} 
   %\setcaptionwidth{6in}
   \vspace{-1cm}
   \caption{Margin and Hausdorff illustration for ridges obtained from {\it l}-SCRE and SCRE}
   \label{fig:circle6}
\end{figure}

@@

\begin{table}[h]
\caption{The margin and Hausdorff between $\cal \hat{G}$ and $\mathcal M$ vary with $h$ for SCRE, {\it l}-SCRE, MFIT-i and MFIT-ii on the 1-dimensional circle}.
\resizebox{14cm}{!}{
\label{result_compare}
\begin{tabular}{c|c|ccccccccc}\hline
  & $h$   & 0.1   &0.2 &0.3 &0.4&0.5&0.6&0.7&0.8&0.9\\\hline
  \multirow{4}{*}{Marg}  &SCRE 
& 0.0089 & 0.0103 & 0.0237 & 0.0431 & 0.0702 & 0.1080 & 0.1642 & 0.2569 & 0.4307 \\
  &{\it l}-SCRE
 & 0.0089 & 0.0079 & 0.0083 & 0.0087 & 0.0088 & 0.0089 & 0.0090 & 0.0090 & 0.0091 \\
  &MFIT-i
& 0.0240 & 0.0092 & 0.0076 & 0.0087 & 0.0134 & 0.0200 & 0.0276 & 0.0367 & 0.0473 \\
  &MFIT-ii
& 0.0263 & 0.0113 & 0.0107 & 0.0119 & 0.0155 & 0.0210 & 0.0278 & 0.0356 & 0.0438 \\
  \hline
\multirow{4}{*}{Haus}  &SCRE
& 0.0272 & 0.0265 & 0.0392 & 0.0599 & 0.0875 & 0.1264 & 0.1875 & 0.2979 & 0.5251 \\
  &{\it l}-SCRE
& 0.0273 & 0.0244 & 0.0253 & 0.0256 & 0.0257 & 0.0258 & 0.0258 & 0.0258 & 0.0259 \\
  &MFIT-i
& 0.1164 & 0.0278 & 0.0242 & 0.0260 & 0.0282 & 0.0351 & 0.0443 & 0.0544 & 0.0650 \\
  &MFIT-ii
 & 0.1165 & 0.0461 & 0.0252 & 0.0261 & 0.0332 & 0.0412 & 0.0494 & 0.0583 & 0.0710 \\
 \hline
\end{tabular}}
\end{table}

\begin{table}[h]
\caption{The margin and Hausdorff between $\cal \hat{G}$ and $\mathcal M$ vary with $h$ for SCRE, {\it l}-SCRE, MFIT-i and MFIT-ii on the 2-dimensional sphere}.
\resizebox{14cm}{!}{
\label{result_compare2}
\begin{tabular}{c|c|ccccccccc}\hline
  & $h$   & 0.1   &0.2 &0.3 &0.4&0.5&0.6&0.7&0.8&0.9\\\hline
  \multirow{4}{*}{Marg}  &SCRE 
& 0.0296 & 0.0304 & 0.0557 & 0.0955 & 0.1552 & 0.2478 & 0.4155 & 0.7002 & 0.3371 \\
  &{\it l}-SCRE
& 0.0274 & 0.0272 & 0.0323 & 0.0348 & 0.0360 & 0.0366 & 0.0371 & 0.0373 & 0.0375 \\
  &MFIT-i
& 0.1117 & 0.0409 & 0.0305 & 0.0228 & 0.0305 & 0.0457 & 0.0639 & 0.0849 & 0.1098 \\
  &MFIT-ii
& 0.0288 & 0.0357 & 0.0332 & 0.0285 & 0.0327 & 0.0444 & 0.0591 & 0.0763 & 0.0951 \\  \hline
\multirow{4}{*}{Haus}  &SCRE
& 0.1485 & 0.0891 & 0.0977 & 0.1303 & 0.1915 & 0.3047 & 0.5106 & 0.8972 & 0.9847 \\
  &{\it l}-SCRE
& 0.2012 & 0.0915 & 0.0799 & 0.0790 & 0.0800 & 0.0817 & 0.0827 & 0.0833 & 0.0837 \\
  &MFIT-i
& 0.9114 & 0.4856 & 0.1323 & 0.1129 & 0.0761 & 0.0849 & 0.0990 & 0.1191 & 0.1443 \\
  &MFIT-ii
& 0.1117 & 0.1201 & 0.1384 & 0.1648 & 0.1280 & 0.1146 & 0.1360 & 0.1417 & 0.1786 \\
 \hline
\end{tabular}}
\end{table}

>>>>

For each point $\hat{x}$ belonging to ${\cal \hat{G}}$ or ${\cal \hat{G}}_\ell$, we can define the projection of $\hat{x}$ onto the real manifold $\mathcal M$ as $\pi_{\mathcal M}(\hat{x}) = \arg\min_{y\in \mathcal M} \|y-\hat{x}\|_2$. In the case of the special two-dimensional circle, the projection has an explicit form, $\pi_{\mathcal M}(\hat{x}) = \hat{x}/\|\hat{x}\|$. The average margin from $\cal \hat{G}$ or ${ \cal \hat{G}}_\ell$ to $\mathcal M$ is defined as
\[
{\rm Margin}({ \cal \hat{G}, \mathcal M}) =\frac{1}{|{\cal \hat{G}}|}  \sum_{x_k\in  {\cal \hat{G}}} \min_{y\in \mathcal M}\|x_k-y\|_2.
\]
\begin{figure}[h] %  figure placement: here, top, bottom, or page
   \includegraphics[width=\linewidth]{circle9.eps} 
   \includegraphics[width=\linewidth]{sphere8n.eps} 
   %\setcaptionwidth{6in}
   \vspace{-1cm}
   \caption{Margin and Hausdorff illustration for ridges obtained from {\it l}-SCRE and SCRE}
   \label{fig:circle6}
\end{figure}

@@

\begin{table}[h]
\caption{The margin and Hausdorff between $\cal \hat{G}$ and $\mathcal M$ vary with $h$ for SCRE, {\it l}-SCRE, MFIT-i and MFIT-ii on the 1-dimensional circle}.
\resizebox{14cm}{!}{
\label{result_compare}
\begin{tabular}{c|c|ccccccccc}\hline
  & $h$   & 0.1   &0.2 &0.3 &0.4&0.5&0.6&0.7&0.8&0.9\\\hline
  \multirow{4}{*}{Marg}  &SCRE 
& 0.0117 & 0.0159 & 0.0287 & 0.0481 & 0.0756 & 0.1138 & 0.1704 & 0.2641 & 0.4427 \\
  &{\it l}-SCRE
& 0.0116 & 0.0124 & 0.0133 & 0.0137 & 0.0139 & 0.0140 & 0.0141 & 0.0141 & 0.0142 \\
  &MFIT-i
& 0.0203 & 0.0114 & 0.0123 & 0.0160 & 0.0222 & 0.0303 & 0.0401 & 0.0520 & 0.0662 \\
  &MFIT-ii
& 0.0219 & 0.0131 & 0.0102 & 0.0095 & 0.0146 & 0.0224 & 0.0313 & 0.0412 & 0.0519 \\
  \hline
\multirow{4}{*}{Haus}  &SCRE
& 0.0344 & 0.0329 & 0.0436 & 0.0604 & 0.0913 & 0.1310 & 0.1935 & 0.2973 & 0.5027 \\
  &{\it l}-SCRE
& 0.0350 & 0.0289 & 0.0307 & 0.0322 & 0.0331 & 0.0336 & 0.0339 & 0.0341 & 0.0342 \\
  &MFIT-i
& 0.0952 & 0.0383 & 0.0303 & 0.0347 & 0.0393 & 0.0441 & 0.0531 & 0.0643 & 0.0828 \\
  &MFIT-ii
& 0.1058 & 0.0393 & 0.0306 & 0.0266 & 0.0336 & 0.0426 & 0.0560 & 0.0675 & 0.0740 \\
 \hline
\end{tabular}}
\end{table}

\begin{table}[h]
\caption{The margin and Hausdorff between $\cal \hat{G}$ and $\mathcal M$ vary with $h$ for SCRE, {\it l}-SCRE, MFIT-i and MFIT-ii on the 2-dimensional sphere}.
\resizebox{14cm}{!}{
\label{result_compare2}
\begin{tabular}{c|c|ccccccccc}\hline
  & $h$   & 0.1   &0.2 &0.3 &0.4&0.5&0.6&0.7&0.8&0.9\\\hline
  \multirow{4}{*}{Marg}  &SCRE 
& 0.0320 & 0.0320 & 0.0558 & 0.0963 & 0.1560 & 0.2474 & 0.4062 & 0.6370 & 0.2451 \\
  &{\it l}-SCRE
& 0.0288 & 0.0292 & 0.0333 & 0.0357 & 0.0369 & 0.0376 & 0.0380 & 0.0383 & 0.0385 \\
  &MFIT-i
& 0.1429 & 0.0474 & 0.0297 & 0.0251 & 0.0325 & 0.0467 & 0.0645 & 0.0848 & 0.1097 \\
  &MFIT-ii
& 0.0292 & 0.0315 & 0.0330 & 0.0304 & 0.0310 & 0.0412 & 0.0558 & 0.0738 & 0.0924 \\
\hline
\multirow{4}{*}{Haus}  &SCRE
& 0.1478 & 0.0803 & 0.1070 & 0.1542 & 0.2114 & 0.3139 & 0.4923 & 0.7778 & 0.9165 \\
  &{\it l}-SCRE
& 0.0904 & 0.0828 & 0.0839 & 0.0907 & 0.0937 & 0.0952 & 0.0960 & 0.0966 & 0.0970 \\
  &MFIT-i
& 0.8873 & 0.7947 & 0.1251 & 0.1047 & 0.0806 & 0.0851 & 0.1024 & 0.1271 & 0.1594 \\
  &MFIT-ii
& 0.1127 & 0.1237 & 0.1723 & 0.1874 & 0.1440 & 0.1524 & 0.1636 & 0.1753 & 0.1791 \\
 \hline
\end{tabular}}
\end{table}
